---
title: "SDS 192-01 PS07: Titantic Regraphing"
author: "Sena Amuzu"
date: "12/01/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( echo = TRUE)

library(ggplot2)
library(dplyr) 
library(fivethirtyeight)
# For reading CSV spreadsheet files: 
library(readr)

```

# Regraphing Example: Number of Individuals in each Class on the Titanic

The **titanic dataset** from the internet contains demographic information about the 2201 passenengers on the Titanic disaster. *Note there are 2201 rows in this data, one for each passenger.* The information provided includes...

- passenger_number
- Class (1st, 2nd, 3rd, Crew)
- Sex (Female, Male)
- Age (Adult, Child)
- Survived (No, Yes)
 

```{r, echo=FALSE}
titanic <- read_csv("https://rudeboybert.github.io/SDS192/static/PS/titanic.csv")
```

## a) Number of Titanic Passengers in each Class 

**Dplyr commands** are used to output a table that displays the counts of each Class. 

```{r}
titanic_classification <- titanic %>% 
  group_by(Class) %>% 
  summarize(Total = sum(n()))
```

### Graph of Number of Titanic Passengers in each Class
```{r}
ggplot(titanic_classification, aes(x = Class, y = Total)) +
  geom_bar(stat="identity", fill ="steelblue") + 
  ggtitle("Number of Titanic Passengers in each Class", subtitle = "Not Distinguished by Gender") + 
  labs(x = "Passenger Class", y = "Total Passengers")
```

## b) Number of Titanic Passengers in each Class Split by Sex

**Dplyr commands** are used output a table that displays the counts of each Class. *split by sex* 

```{r}
titanic_classification_gender <- titanic %>% 
  group_by(Sex,Class) %>% 
  summarize(Total = sum(n()))
```

### Graph of Number of Titanic Passengers in each Class, Split by Sex
```{r}
ggplot(titanic_classification_gender, aes(x = Class, y = Total, fill = Sex)) +
  geom_bar(stat="identity") + 
  ggtitle("Number of Titanic Passengers in each Class", subtitle = "Distinguished by Gender") + 
  labs(x = "Passenger Class", y = "Total Passengers")
```

 *In every class males out numbered female, especially in the Crew category. I assume this is due to most of the crew jobs being laborious.*  
